### 2017-02-10 chapters/ch2-checkpoint.tex
Existence testing

@@

\section{Fraud detection}

@@

>>>>

\item We define
  $$\texttt{getr}: C_i \rightarrow \mathbb{R}_{\ge 1}$$
  as a function that gets the consensus round number used to create the given CP
  block.

\item The CP blocks that follows a pair of TX blocks must be created using the
  same $\mathcal{C}_r$, otherwise the transaction is invalid. Concretely, given
  a pair $t_{i,j}$ and $t_{i',j'}$, then there exist $c_{i, k}$ and $c_{i', k'}$
  where $j < k$, $j' < k'$, $\{ \texttt{typeof}(b_{i, x}) : x \in \{j, \dots k -
  1\}\}$ are all $\tau$, $ \{ \texttt{typeof}(b_{i', x}) : x \in \{ j', \dots k'
  - 1\} \}$ are all $\tau$ and $\texttt{getr}(c_{i, k}) = \texttt{getr}(c_{i',
    k'})$. This constraint is not the result of the consensus protocol, but the
  validation protocol.

@@

\section{Fraud detection}
Fraud detection is application specific. In the context of electronic cash, a
fraudulent transaction will have an effect in subsequent transactions. In the
context of P2P file sharing, the transactions are reports of the number of bytes
uploaded and/or downloaded, thus they are independent of each other.

We focus in the latter case, where trasactions are independent.

@@

\subsection{Existence testing}
Suppose node $i$ created a TX $t_{i,j}$ and its pair is $t_{i',j'}$. Our
protocol states that there exist two CP block $c_{i,k}$ and $c_{i',k'}$ such
that $k>j$ and $k' > j'$, but all blocks between $(k, j)$ and $(k', j')$ are of
type $\tau$. To verify whether $t_{i', j'}$ exists, $i$ performs the following
tasks:
\begin{enumerate}
\item Waits for $c_{i', k'}$ to be in consensus.
\item Finds $c_{i', k''}$ such that $k'' < j' < k'$ and $k''$ is also in
  consensus (in some previous consensus round).
\item Asks $i'$ for $\{b_{i', x} : x \in \{ k'', \dots k' \}\}$, and verified
  that all the blocks follow the rules of TrustChain and contains $t_{i', j'}$.
\end{enumerate}
